### 2019-07-17 manuscript.tex
Update manuscript.tex

\jdcmt{I've been talking with Mike and Katie about writing papers that are easy to read. You should focus on paragraph structure, particularly the first s. of each \P. I will send you a link.}

\jdcmt{This is a run-on sentence It is estimated,} based on a UNICEF global database \jdcmt{cite the database right here?} including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East. \jdcmt{Can this be a new sentence? are the 15 million also girls below 15? If so, link directly and if not, clarify} and 44 million of them are girls below age 15, with another 15 million girls at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Progress in reducing FGC is not keeping up with the population growth: the number of girls and women undergoing FGC  is projected to rise significantly over the next decade if current trends continue \cite{KhosBane17, UNIC16}.
\jdcmt{Need to think about how much to about terminology and how to say it} FGC is also known as female genital mutilation and female circumcision.  As adapted by Tostan \cite{Tost15}, \jdcmt{I don't understand any of this. Can you just say Tostan and others suggest cutting? Why can't this be put into the first s?} cutting is preferred over circumcision without diminishing or excusing the negative impact of the practice because it implies a degree of self-awareness and is considered less judgmental  \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}

\jdcmt{Wordy: ``about eradication'' is indirect} The commonly shared position for the practice of FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update} \jdcmt{Simplify: it looks like there's been a consensus for eradication for decades.} .  The progress is hindered due to the complicated history of the \jdcmt{what does this mean? very practice} \cite{BergDeni12, Cami16}. The meanings of FGC are \jdcmt{don't understand: competitively defined by various groups from local religious community to international governmental institutes, and by linking the practice to cultural and religious identity in one end and to public health and human rights on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding values and norms \jdcmt{you introduce norms soon, is it weird to use them now?} attached to FGC practice is essential to comprehend the persistence of FGC practice \cite{}.  Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in comprehending,  intervening or eradicating the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} \cfonly{more cites}.
\jdcmt{Not sure what is the relation in terms of document flow between the s. above and the s. below.}

Social norm is often used to understand behavioural pattern of FGC \cfonly{more cite{BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17, Youn02} (to confirm)}.  Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} \cfonly{Bicc etc, more}.  Convention theory, a widely \jdcmt{not sure what this word means; inferred} approach in FGC research, posits that FGC is an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group coordination, \jd{s. starting to run on} and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC is also viewed as social capital for inclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \jdcmt{this seems circular; self-enforcing is the definition of norms} \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.

@@

>>>>

It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.  It was also foreseen that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Progress in reducing FGC is not keeping up with the population growth: the number of girls and women undergoing FGC is projected to rise significantly over the next decade if current trends continue \cite{KhosBane17, UNIC16}.  Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}

In most part of the world, FGC is defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.  The commonly shared position of FGC is about to abolish than to intervene the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.  Yet, the progress of intervention is hindered due to the complicated history \cite{BergDeni12, Cami16}.  FGC is embodied with multiple meanings with cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding values and meanings attached to FGC is essential to comprehend the persistence of FGC practice \cite{}.  Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in fathoming the behaviour for intervention \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.

Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} \cfonly{Bicc etc, more}.  Convention theory, a widely \jdcmt{not sure what this word means; inferred} approach in FGC research, posits that FGC is an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group coordination, \jd{s. starting to run on} and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC is also viewed as social capital for inclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \jdcmt{this seems circular; self-enforcing is the definition of norms} \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.

@@

\cfonly{Jonathan:”The explanation of community belief is that it's left over
after we include community behaviour. If the community believes in it,
they'll probably do it, and then I'll probably do it. But if I
_control for_ community behaviour, there's no reason to think that
community belief is still explanatory. In fact, if I see myself as
different from the community I'm more likely to break the norm than if
I don’t.”
}
